% arara: clean: {files: [main.aux, main.idx, main.ilg, main.ind, mainmain.bbl, main.bcf, main.blg, main.run.xml, main.fdb_latexmk, main.fls, main.loe, main.lof, main.lol, main.lot, main.ltb, main.out, main.toc, main.upa, main.upb, main.acn, main.acr, main.alg, main.glg, main.glo, main.gls, main.glsdefs, main.idx,  main.ilg, main.xdy, main.loa, main.gnuploterrors , main.mw, main.fdb_latexmk ]}
% arara: pdflatex: {shell: yes}
% arara: makeglossaries
% arara: makeindex: {style: main.ist }
% !arara: bibtex
% arara: pdflatex: {shell: yes}
% arara: pdflatex: {shell: yes}
% arara: clean: {files: [main.aux, main.idx, main.ilg, main.ind, main.bbl, main.bcf, main.blg, main.run.xml, main.fdb_latexmk, main.fls, main.loe, main.lof, main.lol, main.lot, main.ltb, main.out, main.toc, main.upa, main.upb, main.acn, main.acr, main.alg, main.glg, main.glo, main.gls, main.glsdefs, main.idx,  main.ilg, main.xdy, main.loa, main.gnuploterrors , main.mw, main.fdb_latexmk ]}


\documentclass[epsbased,copyright,final,covers,extendedindex,firstnumbered,tfg,gnuplot]{main}
\usepackage{pdfpages}
\usepackage{tikz,color}
\usepackage{pgf-pie}
\usepackage{bchart}
\usepackage{rotating}
\usepackage{glossaries}
\usepackage{amsmath}
\usepackage{booktabs}
\setlength{\abovedisplayskip}{12pt}
\setlength{\belowdisplayskip}{12pt}

% REVISE
\usepackage{longtable}
\usepackage{lscape}
\usepackage[export]{adjustbox}
% \usepackage{geometry}

\advisor{Lara Quijano-Sánchez}
\levelin{Computer Engineering}
\title{Author Profiling}
\subtitle{An analysis of the differences in writing styles in formal and informal texts}
\author{Luna Mancebo Rodríguez}
\privateaddress{C\textbackslash\ Francisco Tomás y Valiente nº 11}
\copyrightdate{20 de marzo de 2023}

% \dedication{A mis amigas}
% \famouscite{For most of history, Anonymous was a woman.\\[0.1em]
% \begin{flushright}Virginia Woolf\end{flushright}}

\makeglossaries
\newacronym{API}{API}{Application Programming Interface.}
\newacronym{BERT}{BERT}{Bidirectional Encoder Representations from Transformers.}
\newacronym{BILTSM}{BILTSM}{Bidirectional Long Short-Term Memory.}
\newacronym{CNN}{CNN}{Convolutional Neural Network.}
\newacronym{RNN}{RNN}{Recurrent Neural Network.}
\newacronym{DNN}{DNN}{Deep Neural Network.}
\newacronym{DT}{DT}{Decision Tree.}
\newacronym{KNN}{KNN}{K-Nearest Neighbours.}
\newacronym{LDA}{LDA}{Latent Dirichlet Allocation.}
\newacronym{LR}{LR}{Logistic Regression.}
\newacronym{LSTM}{LSTM}{Long Short-Term Memory.}
\newacronym{ML}{ML}{Machine Learning.}
\newacronym{NB}{NB}{Naive Bayes.}
\newacronym{NLP}{NLP}{Natural Language Processing.}
\newacronym{RF}{RF}{Random Forest.}
\newacronym{SVM}{SVM}{Support Vector Machine.}
\newacronym{XGBoost}{XGBoost}{eXtreme Gradient Boosting.}
\newacronym{FE}{FE}{Feature engineering.}
\newacronym{RegLog}{RegLog}{Logistic Regression.}
\newacronym{MLP}{MLP}{Multilayer Perceptron.}
\newacronym{PDF}{PDF}{Probability Density Function.}
\newacronym{BoW}{BoW}{Bag of Words.}
\newacronym{TF-IDF}{TF-IDF}{Term Frequency - Inverse Document Frequency.}
\newacronym{AIA}{AIA}{Artificial Intelligence Act}
\newacronym{BiGRU}{BiGRU}{Bidirectional Gated Recurrent Unit}
\newacronym{GBDT}{GBDT}{Gradient Boosted Decision Trees}
\newacronym{LSA}{LSA}{Latent Semantic Analysis}
\newacronym{AI}{AI}{Artificial Intelligence}

%\prefacefile{inicio/prefacio}
\ackfile{init/acknowledgments}
\resumenfile{init/summary}
\abstractfile{init/abstract}

\keywords{Algunas}
\palabrasclave{Otras}

\coverdata
{
  Escuela Politécnica Superior \\
  Universidad Autónoma de Madrid \\
  C\textbackslash Francisco Tomás y Valiente nº 11
}


\usepackage[numbers]{natbib}
\bibliographyconfig[abbrvnat]{main}
% \usepackage{natbib}
% \usepackage[natbibapa]{apacite} 
% \setcitestyle{authoryear,open={(},close={)}} %Citation-related commands

% \usepackage{apacite}
% \bibliographystyle{apacite}
% \bibliographystyle{abbrvnat}

\datadir{data}
\graphicsdir{img}
\logosdir{img}
\codesdir{codes}

\begin{document}

%1
\chapter{Introduction\label{CAP:INTRODUCTION}}{intro/introduction}
%2
\chapter{State of the Art\label{CAP:STATEOFTHEART}}{StateOfTheArt/stateoftheart}
%2
\chapter{Methods\label{CAP:METHODS}}
\section{Datasets\label{SEC:DATASETS}}{Methods/datasets}
\section{Data pre-processing\label{SEC:DP}}{Methods/dataPreprocessing}
\section{Feature selection\label{SEC:FS}}{Methods/featureExtraction}
\printglossary

\end{document}
